Meta-analysis

### 2020-06-02 04_MetaAnalysis.Rmd
Remove MSE imputation Slice out trials with no variation formatting and spelling edits Change a few chunks so they are not evaulated Use labbeller function to rename facets in plots

```{r imputation_MSE}
for (i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), ]$trial_ref) {
   slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "Y_Msquare"] <-
      exp(rnorm(
         n = 1,
         mean = mean(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE),
         sd(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE)
      ))
}
```

@@

```{r treatment_means_plot}
# class spray_managment as a factor and reorder them for the plot
slimmer_PM_dat$spray_management <-
   factor(slimmer_PM_dat$spray_management,
          levels(factor(slimmer_PM_dat$spray_management))[rev(c(1, 2, 4, 5, 3))])

@@

## Meta-analysis  
### metafor package  
Let's load the metafor package we are using to analyse the data, then rearrange the factors we want to examine by placing the control treatment first. This way all treatments will be compared to the no spray controls.  
Next we are log transforming the grain yield and calculating the variance from the trial mean squares.  
Finally we will assign factor classes to the main variables in the meta-analysis. Note that variable trial is a combination of:

@@

```{r Initiak_ReRunMetafor}
dat1 <- data.frame(
   iteration = 0,
   mods = names(coef(PM_mv_AI)),
   coefs = coef(PM_mv_AI),
   se = PM_mv_AI$se,
   zval = PM_mv_AI$zval,
   pval = PM_mv_AI$pval,
   ci.lb = PM_mv_AI$ci.lb,
   ci.ub = PM_mv_AI$ci.ub,
   row.names = NULL
   )

write.csv(dat1, "./cache/metaIteration.csv", row.names = FALSE)
```

```{r run_iterations_asJobscript}
# WARNING don't run a high number of iterations without increasing sys.sleep
# sys.sleep should not be reduced below 4 for 50 iterations and
# below 0.5 for 10 iterations
for(ITERATE in 1:10){
rstudioapi::jobRunScript(
  "./R/ReRun_metafor-grainyield.R",
  workingDir = here::here(),
  name = "metafor_iteration",
)
   Sys.sleep(1)
}
```

```{r coef_iteration}
dat1 <- read.csv("./cache/metaIteration.csv")
table(dat1$iteration)
dat1 %>%
   ggplot(aes(x = iteration ,y = coefs,))+
   geom_ribbon(aes(ymax = ci.ub, ymin = ci.lb, x = iteration), fill = "grey70")+
   geom_line()+
   facet_grid(cols = vars(mods))

@@

```{r pval_iteration_plot}
dat1 %>%
   ggplot(aes(x = iteration ,y = pval,))+
   geom_line()+
   geom_hline(yintercept = 0.05, colour = "grey50", linetype = 2)+
   facet_grid(cols = vars(mods))

The first table in this output shows the tau^2 (variance) of each random effects and the number of occurrences for each treatment in the analysis. The second table is in two parts(left and right). The left part indicates the level of acceptable rho (variation) when comparing treatments. All comparisons were acceptable except for a comparison between `Early` and `Late_plus`, `0.000` rho. `Early` and `Late_plus` treatments never occured within the same trial which is indicated by the right side of the table.

@@

To make it easier to compare each of the treatments we can compute the meta-analysis contrasts.
```{r metafor_contrasts}
anova(PM_mv_AI, L = rbind(
   c(0, 1, -1, 0, 0),
   # early vs Recomended
   c(0, 1, 0, -1, 0),
   # early vs recommended plus
   c(0, 1, 0, 0, -1),
   # early vs Late plus
   c(0, 0, -1, 1, 0),
   # Recommended plus vs recommended
   c(0, 0, -1, 0, 1),
   # Late_Plus vs Recommended
   c(0, 0, 0, -1, 1)
)) # Late_plus vs Recommended plus
```
Results show with the exclusion of the no spray control, none of the treatments are significantly different, however, early applications treatments on average produced lower yields. Also the model was almost significant when assessing recommended_plus as saving more yield than recommended. This is probably due to the fact there were more comparisons between these two treatments which allowed a more certain outcome.
Let's view these comparisons in a plot.

>>>>

```{r imputation_MSE, eval=FALSE, include=FALSE}
for (i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), ]$trial_ref) {
   slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "Y_Msquare"] <-
      exp(rnorm(
         n = 1,
         mean = mean(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE),
         sd(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE)
      ))
}
```

The use of these imputed MSE was giving a varied outcome each time it was run. We the next code chunk removes the studies without variation to observe what the meta-analysis outcome would be.

```{r remove_NA_MSE}
slimmer_PM_dat <- 
   slimmer_PM_dat[!is.na(slimmer_PM_dat$Y_Msquare),]

@@

```{r treatment_means_plot}
# class spray_management as a factor and reorder them for the plot
slimmer_PM_dat$spray_management <-
   factor(slimmer_PM_dat$spray_management,
          levels(factor(slimmer_PM_dat$spray_management))[rev(c(1, 2, 4, 5, 3))])

@@

## Meta-analysis  
### metafor package  
Let's load the `metafor` package we are using to analyse the data, then rearrange the factors we want to examine by placing the control treatment first. This way all treatments will be compared to the no spray controls.  
Next we are log transforming the grain yield and calculating the variance from the trial mean squares.  
Finally we will assign factor classes to the main variables in the meta-analysis. Note that variable trial is a combination of:

@@

```{r Initiak_ReRunMetafor, eval=FALSE, include=FALSE}
dat1 <- data.frame(
   iteration = 0,
   mods = names(coef(PM_mv_AI)),
   coefs = coef(PM_mv_AI),
   se = PM_mv_AI$se,
   zval = PM_mv_AI$zval,
   pval = PM_mv_AI$pval,
   ci.lb = PM_mv_AI$ci.lb,
   ci.ub = PM_mv_AI$ci.ub,
   row.names = NULL
   )

# commented the code below so the file does not get overwritten
#write.csv(dat1, "./cache/metaIteration.csv", row.names = FALSE)
```

```{r run_iterations_asJobscript, eval=FALSE, include=FALSE}
# WARNING don't run a high number of iterations without increasing sys.sleep
# sys.sleep should not be reduced below 4 for 50 iterations and
# below 0.5 for 10 iterations
for(ITERATE in 1:10){
rstudioapi::jobRunScript(
  "./R/ReRun_metafor-grainyield.R",
  workingDir = here::here(),
  name = "metafor_iteration",
)
   Sys.sleep(1)
}
```

```{r coef_iteration}
change_labels <- function(x1){
   x1 <- gsub(pattern = "spray_management",replacement = "",x = x1)
   x1 <- gsub(pattern = "_",replacement = "\n",x = x1)
   x1
}

dat1 <- read.csv("./cache/metaIteration.csv")
dat1 %>%
   ggplot(aes(x = iteration ,y = coefs,))+
   geom_ribbon(aes(ymax = ci.ub, ymin = ci.lb, x = iteration), fill = "grey70")+
   geom_line()+
   facet_grid(cols = vars(mods), labeller = labeller(mods = change_labels))+
   theme(strip.text.x = element_text(size = 9))

@@

```{r pval_iteration_plot}
dat1 %>%
   ggplot(aes(x = iteration ,y = pval,))+
   geom_line()+
   scale_y_log10()+
   geom_hline(yintercept = 0.05, colour = "grey50", linetype = 2)+
   facet_grid(cols = vars(mods), labeller = labeller(mods = change_labels))+
   theme(strip.text.x = element_text(size = 9))

temp_labels(dat1)
labeller()
```

The first table in this output shows the tau^2 (variance) of each random effects and the number of occurrences for each treatment in the analysis. The second table is in two parts(left and right). The left part indicates the level of acceptable rho (variation) when comparing treatments. All comparisons were acceptable except for a comparison between `Early` and `Late_plus`, `0.000` rho. `Early` and `Late_plus` treatments never occurred within the same trial which is indicated by the right side of the table.

@@

To make it easier to compare each of the treatments we can compute the meta-analysis contrasts.
```{r metafor_contrasts}
anova(PM_mv_AI, L = rbind(
   c(0, 1, -1, 0, 0),
   # early vs Recommended
   c(0, 1, 0, -1, 0),
   # early vs recommended plus
   c(0, 1, 0, 0, -1),
   # early vs Late plus
   c(0, 0, -1, 1, 0),
   # Recommended plus vs recommended
   c(0, 0, -1, 0, 1),
   # Late_Plus vs Recommended
   c(0, 0, 0, -1, 1)
)) # Late_plus vs Recommended plus
```
Results show with the exclusion of the no spray control, none of the treatments are significantly different, however, early applications treatments on average produced lower yields. Also the model was almost significant when assessing recommended_plus as saving more yield than recommended. This is probably due to the fact there were more comparisons between these two treatments which allowed a more certain outcome.
Let's view these comparisons in a plot.
